### 2015-02-22 fundamentals/impl.tex
the new intro sentence already made the arbitrary facility comment
the removed... too picky?

The \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter the simulation at arbitrary
times and trade in discrete resources. These resources are not defined \textit{a
  priori}. Therefore, the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which
\Cyclus simulations are built.  As the \Cyclus supply-demand resolution
framework, the DRE must be able to support arbitrary facilities. Supporting the
general \Cyclus philosophy, facilities are treated as black boxes and a clear
supply-demand communication framework is defined.

@@

\subsection{Simulation Support}
So that users and developers can build working simulations
in the shortest time possible, the \Cyclus ecosystem provides the fundamental
building blocks: basic archetypes and a toolkit of commonly needed functions.
The \Cycamore library provides a suite of fundamental Region, Institution, and
Facility archetypes, while the \Cyclus toolkit provides assistance to
developers.

>>>>

The \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter the simulation at arbitrary
times and trade in discrete resources. These resources are not defined \textit{a
  priori}. Therefore, the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which
\Cyclus simulations are built.  Supporting the general \Cyclus philosophy,
facilities are treated as black boxes and a clear supply-demand communication
framework is defined.

@@

\subsection{Simulation Support}
So that users and developers can build working simulations in the shortest time
possible, the \Cyclus ecosystem provides fundamental building blocks: basic
archetypes and a toolkit of commonly needed functions.  The \Cycamore library
provides a suite of fundamental Region, Institution, and Facility archetypes,
while the \Cyclus toolkit provides assistance to developers.
